---
title: "Runoff Volumes"
author: "Ruth Enriquez"
date: "2022-08-12"
output: html_document
---

#Attach the tidyverse and here packages

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(here)
```

#Source your storm_runoff.R script so you are able to use the predict_runoff function in your .Rmd

```{r}
source(here::here("src", "storm_runoff.R"))
```

#In a code chunk in your runoff_volumes.Rmd, use your predict_runoff function to estimate stormwater volume for a watershed of 182 acres, over a range of estimates for the impervious fraction (from 0.6 to 0.8, by increments of 0.01). Note: you do not need to write a for loop here.

#Bind your sequence of impervious fractions together with the resulting runoff volume calculated into a data frame

```{r}
impervious_fraction <- seq(from = 0.6, to = 0.8, by = 0.01)

runoff_volumes <- predict_runoff(Ia = impervious_fraction, A = 182)

runoff_df <- data.frame(impervious_fraction, runoff_volumes)
```

# Create a ggplot graph that has both dots and connecting lines (i.e., you’ll layer geom_point() and geom_line(). Update axis labels. Export a png of your graph to the figs folder using ggsave

```{r}
runoff_gg <- ggplot(data = runoff_df, aes(x = impervious_fraction, y = runoff_volumes))+
  geom_point()+
  geom_line()+
  labs(x = "Imprevious Fraction", y = "Runoff Volumes c^3")
```

```{r}
ggsave(plot = runoff_gg, here::here("fig", "runoff_gg.png"),
       width = 5,
       height = 6)
```

